\Title

### 2016-08-20 manuscript/manuscript.tex
Thank the editor and reviewers
Fixes #24
Minor changes to the text

Estimating Moho depth from gravity data is a non-linear inverse problem.
One can generalize this problem of estimating the depths of an interface
separating two media,
such as the sediment-basement interface of a sedimentary basin or the
crust-mantle interface (Moho).
Several methods have been developed over the years to solve this inverse
problem, for example
\citet{bott1960, barbosa1999b, barbosa1999a, barnes2012, leao1996, martins2010,
martins2011, oldenburg1974, reguzzoni2013, santos2015, silva2006, silva2014},
to name a few.
Solving the inverse problem is computationally demanding because it requires
the construction of large dense matrices and the solution of large linear
systems.
As a result, some authors search for ways to increase the computational
efficiency of this class of inverse problem.
\citet{bott1960} proposed a method based on iteratively applying corrections to
a starting estimate based on the inversion residuals.
The algorithm is fast because it bypasses the construction and solution of
linear systems and only involves forward modeling.
\citet{oldenburg1974} showed that the fast FFT-based forward modeling of
\citet{parker1973} could be rearranged to estimate the relief.
\citet{barnes2012} use a form of adaptive discretization to compute the
Jacobian, or sensitivity, matrix.
For each data point, the discretization will be progressively coarser
the further way from the point.
This reduces the matrix and, consequently, the linear systems to a sparse form
that can be solved efficiently.
Recently, \citet{silva2014} extended and generalized the original method of
\citet{bott1960} and \citet{santos2015} used this extension to estimate a
basement relief with sharp boundaries.

A spherical Earth approximation is preferred when estimating the Moho depth
from gravity data in continental and global scale studies.
\citet{wieczorek1998} developed a spherical harmonic equivalent of the
Parker-Oldenburg FFT algorithm and applied it to estimate the crustal structure
of the Moon.
\citet{reguzzoni2013} use a spherical Earth approximation to estimate the
global Moho relief using data from the GOCE satellite mission.
Another approach is to use
non-spectral (space domain) gravity inversion methods.
Many such methods were developed for estimating the basement relief of a
sedimentary basin
\citep[e.g., ][]{barbosa1999a, barbosa1999b, martins2010, martins2011, sun2014}.
These methods approximate the sedimentary pack by a set of juxtaposed
right-rectangular prisms.
The top of the prisms coincide with the Earth's surface and the prisms'
thicknesses represent the depths to the basement and are the parameters to be
estimated in the inversion.
The use of rectangular prisms implies a planar Earth approximation and may not
be adequate for depth-to-Moho estimates in a continental-scale study.
A straightforward way to circumvent this hindrance is to adapt one of the
methods developed for rectangular prisms to use tesseroids (spherical prisms).
One of the difficulties of this approach is that the forward problem for a
tesseroid must be solved numerically.
Two alternatives proposed in the literature to the numerical solution are
Taylor series expansion \citep{heck2007, grombein2013}
and the Gauss-Legendre Quadrature
\citep{asgharzadeh2007}.
Numerical experiments by \citet{wild-pfeiffer2008} suggest that the
Gauss-Legendre Quadrature (GLQ) offers superior results.
However, the GLQ suffers from numerical instability when the computation point
is close to the tesseroid \citep{asgharzadeh2007}.
To overcome the numerical instability, \citet{li2011} proposed an adaptive
discretization algorithm which was later improved upon by \citet{uieda2016}.

@@

\noindent
where $\mathbf{I}$ is the identity matrix.
In this framework,
Bott's method uses a Bouguer plate approximation of the gravitational effect of
the relief, $d_i = 2\pi G \Delta\rho z_i$.
The derivative of $d_i$ with respect to the parameter $z_i$ is
$2\pi G \Delta \rho$, thus linearizing the Jacobian matrix.
However, the non-linearity of the predicted data $\mathbf{d}(\mathbf{p}^k)$ is
preserved.

@@

We propose a regularized version of Bott's method to invert gravity data for
estimating the depth of the Moho in spherical coordinates.
To adapt Bott's method to spherical coordinates,
we replace the right-rectangular prisms in the forward modeling
($\mathbf{d}(\mathbf{p}^k)$ in Eq.~\ref{eq:bott})
with tesseroids.
The tesseroid forward modeling uses the adaptive discretization algorithm
of \citet{uieda2016} to achieve accurate results.
Furthermore, our formulation maintains the regularized solution
for the Gauss-Newton method (Eq.~\ref{eq:gaussnewton-regul})
but replaces the full Jacobian matrix with the Bouguer plate approximation
(Eq.~\ref{eq:bott-gaussnewton}).
Here, the Jacobian matrix is a diagonal matrix whose elements are invariant
along successive iterations.
Using this approximation eliminates the cost of computing and storing
the full $N \times M$-dimensional Jacobian matrix $\mathbf{A}^k$ at each
iteration
(Eq.~\ref{eq:jacobian}).
Traditionally, the Jacobian matrix is computed using a first-order finite
difference scheme,
which requires $2 \times N \times M$ forward modeling operations per iteration.
Using Eq.~\ref{eq:bott-gaussnewton} requires $N$ multiplications that need only
be performed once.
This provides a considerable speed gain.

@@

The main computational advantage of our formulation is that it retains the
efficiency of Bott's method while stabilizing the solution through the well
established formalism of Tikhonov regularization.

@@

Fig.~\ref{fig:simple-results}a shows the final estimated Moho depth
after cross-validation.
The recovered model is smooth, indicating that the cross-validation procedure
was effective in estimating an optimal regularization parameter.
Fig.~\ref{fig:simple-results}b shows difference between the true Moho depth
(Fig.~\ref{fig:simple-data}a) and the estimated Moho depth.
The differences appear to be semi-randomly distributed with a maximum
coinciding with a short-wavelength feature in the true model.
The maximum and minimum differences are approximately
2.19 and -2.13 km, respectively.
Fig.~\ref{fig:simple-results}c shows inversion residuals, defined as the
difference between the observed and predicted data (in mGal).
The largest residual (in absolute value) coincides with the largest difference
between the true model and the estimate.
The inversion residuals are normally distributed,
as shown in Fig.~\ref{fig:simple-results}d,
with 0.02 mGal mean and a standard deviation of 3.63 mGal.
The cross-validation curve in Fig.~\ref{fig:simple-results}e
shows a clear minimum MSE at $\mu = 0.00046$
(indicated by the red triangle).
Fig.~\ref{fig:simple-results}f shows the convergence of
the Gauss-Newton optimization in eight iterations.

@@

In this test, we simulate the anomalous Moho of South America
using Moho depth information extracted from the CRUST1.0 model
\citep{laske2013}.
We construct a tesseroid model with
$M_{lat} \times M_{lon} = 80 \times 60$ juxtaposed elements, 4800 in total,
using the Moho depths shown in Fig.~\ref{fig:crust1-data}a.
In our model, the Normal Earth Moho is $z_{ref} = 30\ km$ and
the density-contrast is $\Delta\rho = 350\ kg/m^3$.
We produce the synthetic data at a constant height of 50 km
and on a regular grid of $N_{lat} \times N_{lon} = 159 \times 119$ points
(a total of 18921 observations).
We contaminate the synthetic data with normally distributed pseudo-random noise
with zero mean and 5 mGal standard deviation (Fig.~\ref{fig:crust1-data}b).

@@

The raw gravity data are generated from the satellite only
spherical harmonic model GOCO5S \citet{mayer-guerr2015}.
The GOCO5S model combines data from 15 satellites, including the complete
mission data from the GOCE satellite.
The data were downloaded from the
International Centre for Global Earth Models (ICGEM) web-service
\citep[][ \url{http://icgem.gfz-potsdam.de/ICGEM/})]{barthelmes2012}
in the form of the complete gravity field
on a regular grid with $0.2^\circ$ grid spacing at ellipsoidal height 50 km.
We calculate the gravity disturbance
($\delta(P)$ in Eq.~\ref{eq:disturbance})
by subtracting from the raw data
the normal gravity of the WGS84 reference ellipsoid ($\gamma(P)$)
using the formula of \citet{li2001a}.
Fig.~\ref{fig:sam-corrections}a show the calculated gravity disturbance of
South America.

@@

In the Amazon and Paraná Basins, our model fits the gravity data but
underestimates the seismological data by up to 15 km.
This indicates that a mass excess is present in the crust or upper mantle.
A body with positive density contrast whose gravitational effect was not
removed from the data during processing will make the observed gravity
disturbance greater than it would be otherwise.
This will cause the inversion to produce a shallower Moho estimate.
These discrepancies between gravity and seismological estimates have been noted
before by \citet{nunn1988} for the Amazon Basin and \citet{mariani2013}
for the Paraná Basin.
Both studies propose high density rocks in the lower crust as probable causes
for the discrepancies.
Another possible cause for the observed discrepancy in our model could be our
failure to fully remove from the data the effects of the igneous intrusions
present in both basins.
Using a sediment model for South America more detailed than CRUST1.0
might lead to more accurate results for these basins.

@@

We have developed a computationally efficient gravity inversion method in
spherical coordinates.
Our method extends the Gauss-Newton formulation of Bott's method
\citep{silva2014} to use tesseroids as model elements and Tikhonov
regularization.
The computational efficiency of our method is due to
using Bott's approximation for the Jacobian matrix
(Eq.~\ref{eq:bott-gaussnewton})
and using sparse matrix algorithms for arithmetic operations and the solution
of linear systems.
The Bouguer plate approximation in Eq.~\ref{eq:bott-gaussnewton} is adequate
and the method converges
even when the data are at higher altitudes and the model is not outcropping,
as shown by the applications to synthetic data.
We employ hold-out cross-validation to estimate the regularization parameter
and a validation procedure using seismological data to estimate the Moho
density-contrast and the Normal Earth Moho depth.

There are two main advantages of the proposed method over previous works.
First, unlike the Parker-Oldenburg method \citep{oldenburg1974} or methods
using rectangular prisms, our inversion method does not require the data to be
projected onto a plane.
Second, the Parker-Oldenburg method and methods derived from \citet{bott1960}
\citep[e.g., ][]{silva2014,santos2015} cannot apply the
traditional methodology for constraining inverse problems
described in \citet{silva2001b}.
Our method has no such restriction because we use the formalism of traditional
Tikhonov inversion.
However, the proposed method is not without limitations.
It requires data on a regular grid and restricts the
model to be a regular mesh tied to the data grid.
There is also the limitation that, like \citet{bott1960},
our method only works for gravity disturbances and not the gravity gradients.

The test on simple synthetic data shows that our inversion method is able to
recover a smooth Moho relief with a homogeneous density-contrast.
The inversion was not able to fully recover the shortest wavelength feature in
the model, possibly due to the smoothness constraints which tends to soften
high-frequency (sharp) variations.
The cross-validation Mean Square Error curve in Fig.~\ref{fig:simple-results}e
has a well-defined minimum, indicating a value of the regularization parameter
($\mu$) whose corresponding estimate best predicts data that were not included
in the inversion.
Using this value of $\mu$ in the inversion leads to a stable solution
characterized by a smooth Moho relief with an acceptable data misfit.

The source code profiling results presented in Table~\ref{profiling}
confirm the efficiency of the proposed method.
When using sparse matrices, solving linear systems and performing matrix
multiplications together account for a mere 0.067\% of the total computation
time required for a single inversion.
The majority of the computation time (99.824\%) is spent on forward modeling.
Thus, we are able to retain the high computational efficiency of Bott's method
and use a classic Tikhonov regularization formulation.
This approach could, in theory, be extended to other types of regularization
(e.g., total variation) and misfit functions (e.g., re-weighted least squares)
already available in the literature.
For example, the total variation approach used by \citet{martins2011} could
potentially be implemented in a more straight forward manner than done by
\citet{santos2015}.

The more complex synthetic data test based on CRUST1.0
(Fig.~\ref{fig:crust1-results})
shows that the validation using pointwise Moho depth information
is able to correctly estimate the density-contrast ($\Delta\rho$) and Normal
Earth Moho depth ($z_{ref}$).
This test indicates that the inversion neither correctly estimates Moho depth
nor adequately fits the gravity and pointwise data when sharp variations in
Moho depth occur.
This phenomenon is particularly strong in the region below the Andes.
A likely explanation is that the smoothness regularization
is intrinsically unable to produce sharp variations in Moho depth.
These effects might be mitigated with the use of sharpness-inducing
regularization, like
the weighted smoothness inversion \citep{barbosa1999a},
Cauchy norm regularization \citep{sacchi1996, pilkington2008},
entropic regularization \citep{silva2010},
total variation regularization \citep{martins2011},
or an adaptive mixed smoothness-sharpness regularization \citep{sun2014}.

We applied the method proposed here to estimate the Moho depth for South
America.
Our estimated Moho depth model is in accordance with previous results by
\citet{vandermeijde2013}.
The model fits well the gravity and seismic data in all oceanic regions, the
central portion of the Andean foreland, Patagonia, and coastal and central
parts of Brazil.
However, the model is unable to fit the gravity and seismic data in places with
sharp variations in Moho depth, particularly below the Andes and in the
boundaries of the main geotectonic provinces of the South American Plate, like
the Borborema province, the Parnaiba Basin, and the São Francisco Craton.
This might indicate that smoothness regularization should not be applied
indiscriminately to the whole model, as suggested by the CRUST1.0 synthetic
data test.
Another reason for the observed misfit might be the presence of crustal or
mantle density anomalies whose gravitational effects were not removed during
the data corrections.
In the Guyana Basin on the coastal region of Venezuela, along the central
Amazonas and Solimões Basins, and in the Paraná Basin, our Moho depth model is
able to fit the gravity data but differs significantly from the seismic data.
\citet{mariani2013} and \citet{nunn1988} explain these discrepancies in the
Paraná and Amazonas Basins, respectively, as high density rocks in the lower
crust.
In general, differences between a gravity and a seismically derived Moho model
may indicate the presence of crustal or mantle density anomalies that were
unaccounted for in the data processing.
Such locations warrant further detailed investigation.

@@

We are indebted to the developers and maintainers of the open-source
software without which this work would not have been possible.
We thank Dr. Marcelo Assumpção for providing the seismological Moho depth
estimates.
L. Uieda was supported by a scholarship from
Coordenação de Aperfeiçoamento de Pessoal de Nível Superior
(CAPES).
V.C.F. Barbosa was supported by a fellowship from
Conselho Nacional de Desenvolvimento Científico e Tecnológico (CNPq).

>>>>

Estimating Moho depth from gravity data is a non-linear inverse problem.
One can generalize this problem of estimating the depths of an interface
separating two media,
such as the sediment-basement interface of a sedimentary basin or the
crust-mantle interface (Moho).
Several methods have been developed over the years to solve this inverse
problem, for example
\citet{bott1960, barbosa1997, barbosa1999b, barbosa1999a, barnes2012, leao1996,
martins2010, martins2011, oldenburg1974, reguzzoni2013, santos2015, silva2006,
silva2014},
to name a few.
Solving the inverse problem is computationally demanding because it requires
the construction of large dense matrices and the solution of large linear
systems.
As a result, some authors search for ways to increase the computational
efficiency of this class of inverse problem.
\citet{bott1960} proposed a method based on iteratively applying corrections to
a starting estimate based on the inversion residuals.
The algorithm is fast because it bypasses the construction and solution of
linear systems and only involves forward modeling.
\citet{oldenburg1974} showed that the fast FFT-based forward modeling of
\citet{parker1973} could be rearranged to estimate the relief.
\citet{barnes2012} use a form of adaptive discretization to compute the
Jacobian, or sensitivity, matrix.
For each data point, the discretization will be progressively coarser
the further way from the point.
This reduces the matrix and, consequently, the linear systems to a sparse form
that can be solved efficiently.
Recently, \citet{silva2014} extended and generalized the original method of
\citet{bott1960} and \citet{santos2015} used this extension to estimate a
basement relief with sharp boundaries.

A spherical Earth approximation is preferred when estimating the Moho depth
from gravity data in continental and global scale studies.
\citet{wieczorek1998} developed a spherical harmonic equivalent of the
Parker-Oldenburg FFT algorithm and applied it to estimate the crustal structure
of the Moon.
\citet{reguzzoni2013} use a spherical Earth approximation to estimate the
global Moho relief using data from the GOCE satellite mission.
Another approach is to use
non-spectral (space domain) gravity inversion methods.
Many such methods were developed for estimating the basement relief of a
sedimentary basin
\citep[e.g., ][]{barbosa1997, barbosa1999a, barbosa1999b, martins2010,
martins2011, sun2014}.
These methods approximate the sedimentary pack by a set of juxtaposed
right-rectangular prisms.
The top of the prisms coincide with the Earth's surface and the prisms'
thicknesses represent the depths to the basement and are the parameters to be
estimated in the inversion.
The use of rectangular prisms implies a planar Earth approximation and may not
be adequate for depth-to-Moho estimates in continental- or global-scale study.
A straightforward way to circumvent this hindrance is to adapt one of the
methods developed for rectangular prisms to use tesseroids (spherical prisms).
One of the difficulties of this approach is that the forward problem for a
tesseroid must be solved numerically.
Two alternatives proposed in the literature to the numerical solution are
Taylor series expansion \citep{heck2007, grombein2013}
and the Gauss-Legendre Quadrature
\citep{asgharzadeh2007}.
Numerical experiments by \citet{wild-pfeiffer2008} suggest that the
Gauss-Legendre Quadrature (GLQ) offers superior results.
However, the GLQ suffers from numerical instability when the computation point
is close to the tesseroid \citep{asgharzadeh2007}.
To overcome the numerical instability, \citet{li2011} proposed an adaptive
discretization algorithm which was later improved upon by \citet{uieda2016}.

@@

\noindent
where $\mathbf{I}$ is the identity matrix.
In this framework,
Bott's method uses a Bouguer plate approximation of the gravitational effect of
the relief, $d_i = 2\pi G \Delta\rho\ p_i$.
The derivative of $d_i$ with respect to the parameter $p_i$ is
$2\pi G \Delta \rho$, thus linearizing the Jacobian matrix.
However, the non-linearity of the predicted data $\mathbf{d}(\mathbf{p}^k)$ is
preserved.

@@

We propose a regularized version of Bott's method to invert gravity data for
estimating the depth of the Moho in spherical coordinates.
To adapt Bott's method to spherical coordinates,
we replace the right-rectangular prisms in the forward modeling
($\mathbf{d}(\mathbf{p}^k)$ in Eq.~\ref{eq:bott})
with tesseroids.
The tesseroid forward modeling uses the adaptive discretization algorithm
of \citet{uieda2016} to achieve accurate results.
Furthermore, our formulation maintains the regularized solution
for the Gauss-Newton method (Eq.~\ref{eq:gaussnewton-regul})
but replaces the full Jacobian matrix with the Bouguer plate approximation.
Here, the Jacobian matrix is replaced by a diagonal matrix
(Eq.~\ref{eq:bott-gaussnewton}) whose elements are invariant along successive
iterations.
Using this approximation eliminates the cost of computing and storing
the full $N \times M$-dimensional Jacobian matrix $\mathbf{A}^k$ at each
iteration
(Eq.~\ref{eq:jacobian}).
Traditionally, the full Jacobian matrix is computed using a first-order finite
difference scheme,
which requires $2 \times N \times M$ forward modeling operations per iteration.
Using Eq.~\ref{eq:bott-gaussnewton} requires $N$ multiplications that need only
be performed once.
This provides a considerable speed gain.

@@

The main advantage of our formulation is that it retains the
efficiency of Bott's method while stabilizing the solution through the well
established formalism of Tikhonov regularization.
For example, the total variation approach used by \citet{martins2011} could
potentially be implemented in a more straight forward manner than done by
\citet{santos2015}.

@@

Fig.~\ref{fig:simple-results}a shows the final estimated Moho depth
after the cross-validation.
The recovered model is smooth, indicating that the cross-validation procedure
was effective in estimating an optimal regularization parameter.
Fig.~\ref{fig:simple-results}b shows difference between the true Moho depth
(Fig.~\ref{fig:simple-data}a) and the estimated Moho depth.
The differences appear to be semi-randomly distributed with a maximum
coinciding with a short-wavelength feature in the true model.
The maximum and minimum differences are approximately
2.19 and -2.13 km, respectively.
Fig.~\ref{fig:simple-results}c shows inversion residuals, defined as the
difference between the observed and predicted data (in mGal).
The largest residual (in absolute value) coincides with the largest difference
between the true model and the estimate.
The inversion residuals are normally distributed,
as shown in Fig.~\ref{fig:simple-results}d,
with 0.02 mGal mean and a standard deviation of 3.63 mGal.
The cross-validation curve in Fig.~\ref{fig:simple-results}e
shows a clear minimum MSE at $\mu = 0.00046$
(indicated by the red triangle).
Fig.~\ref{fig:simple-results}f shows the convergence of
the Gauss-Newton optimization in eight iterations.

@@

In this test, we simulate the anomalous Moho of South America
using Moho depth information extracted from the CRUST1.0 model
\citep{laske2013}.
We construct a tesseroid model with
$M_{lat} \times M_{lon} = 80 \times 60$ juxtaposed elements, 4800 in total,
using the Moho depths shown in Fig.~\ref{fig:crust1-data}a.
In our model, the Normal Earth Moho is $z_{ref} = 30\ km$ and
the density-contrast is $\Delta\rho = 350\ kg/m^3$.
We produce the synthetic data at a constant height of 50 km
and on a regular grid of $N_{lat} \times N_{lon} = 159 \times 119$ points
(a total of 18,921 observations).
We contaminate the synthetic data with normally distributed pseudo-random noise
with zero mean and 5 mGal standard deviation (Fig.~\ref{fig:crust1-data}b).

@@

The raw gravity data are generated from the satellite only
spherical harmonic model GOCO5S \citet{mayer-guerr2015}.
The GOCO5S model combines data from 15 satellites, including the complete
mission data from the GOCE satellite.
The data were downloaded from the
International Centre for Global Earth Models (ICGEM) web-service
\citep[][ \url{http://icgem.gfz-potsdam.de/ICGEM/}]{barthelmes2012}
in the form of the complete gravity field
on a regular grid with $0.2^\circ$ grid spacing at ellipsoidal height 50 km.
We calculate the gravity disturbance
($\delta(P)$ in Eq.~\ref{eq:disturbance})
by subtracting from the raw data
the normal gravity of the WGS84 reference ellipsoid ($\gamma(P)$)
using the formula of \citet{li2001a}.
Fig.~\ref{fig:sam-corrections}a show the calculated gravity disturbance of
South America.

@@

In the Amazon and Paraná Basins, our model fits the gravity data but
underestimates the seismological data by up to 15 km.
This indicates that a mass excess may be present in the crust or in the upper
mantle.
A body with positive density contrast whose gravitational effect was not
removed from the data during processing will make the observed gravity
disturbance greater than it would be otherwise.
This will cause the inversion to produce a shallower Moho estimate.
These discrepancies between gravity and seismological estimates have been noted
before by \citet{nunn1988} for the Amazon Basin and \citet{mariani2013}
for the Paraná Basin.
Both studies propose high density rocks in the lower crust as probable causes
for the discrepancies.
Another possible cause for the observed discrepancy in our model could be our
failure to fully remove from the data the effects of the igneous intrusions
present in both basins.
Using a sediment model for South America more detailed than CRUST1.0
might lead to more accurate results for these basins.

@@

We have developed a computationally efficient gravity inversion method in
spherical coordinates.
Our method extends the Gauss-Newton formulation of Bott's method
to use tesseroids as model elements and Tikhonov
regularization.
The computational efficiency of our method is due to
using Bott's approximation for the Jacobian matrix
and using sparse matrix algorithms for arithmetic operations and the solution
of linear systems.
This approximation for the Jacobian matrix is adequate and the method converges
even when the data are at higher altitudes and the model is not outcropping,
as shown by the applications to synthetic data.
We employ hold-out cross-validation to estimate the regularization parameter
and a validation procedure using seismological data to estimate the Moho
density-contrast and the Normal Earth Moho depth.

There are two main advantages of the proposed method over previous works.
First, unlike the Parker-Oldenburg method or methods
using rectangular prisms, our inversion method does not require the data to be
projected onto a plane.
Second, the Parker-Oldenburg method and methods derived from Bott's method
cannot apply the traditional methodology for constraining inverse problems.
Our method has no such restriction because we use the formalism of traditional
Tikhonov inversion.
However, the proposed method is not without limitations.
It requires data on a regular grid and restricts the
model to be a regular mesh tied to the data grid.
Like Bott's method, our method only works for gravity disturbances and not for
the gravity gradients.

The test on simple synthetic data shows that our inversion method is able to
recover a smooth Moho relief with a homogeneous density-contrast distribution.
The inversion was not able to fully recover the shortest wavelength feature in
the model, possibly due to the smoothness constraints which tends to soften
high-frequency (sharp) variations.
The cross-validation Mean Square Error curve has a well-defined minimum,
indicating a value of the regularization parameter ($\mu$) whose corresponding
estimate best predicts data that were not included in the inversion.
Using this value of $\mu$ in the inversion leads to a stable solution
characterized by a smooth Moho relief with an acceptable data misfit.

The efficiency of the proposed method is because solving linear systems and
performing matrix multiplications together account for a mere 0.067\% of the
total computation time required for a single inversion.
The majority of the computation time (99.824\%) is spent on forward modeling.
Thus, we are able to retain the high computational efficiency of Bott's method
and use a classic Tikhonov regularization formulation.
This approach could, in theory, be extended to other types of regularization
(e.g., total variation) and misfit functions (e.g., re-weighted least squares)
already available in the literature.

The more complex synthetic data test based on CRUST1.0
shows that the validation using pointwise Moho depth information
is able to correctly estimate the density-contrast ($\Delta\rho$) and Normal
Earth Moho depth ($z_{ref}$).
This test indicates that the inversion neither correctly estimates Moho depth
nor adequately fits the gravity and pointwise data when sharp variations in
Moho depth occur.
This phenomenon is particularly strong in the region below the Andes.
A likely explanation is that the smoothness regularization
is intrinsically unable to produce sharp variations in Moho depth.
These effects might be mitigated with the use of sharpness-inducing
regularization, like
the weighted smoothness inversion,
Cauchy norm regularization,
entropic regularization,
total variation regularization,
or an adaptive mixed smoothness-sharpness regularization.

We applied the method proposed here to estimate the Moho depth for South
America.
Our estimated Moho depth model is in accordance with previous results.
The model fits well the gravity and seismic data in all oceanic regions, the
central portion of the Andean foreland, Patagonia, and coastal and central
parts of Brazil.
However, the model is unable to fit the gravity and seismic data in places with
sharp variations in Moho depth, particularly below the Andes and in the
boundaries of the main geotectonic provinces of the South American Plate, like
the Borborema province, the Parnaiba Basin, and the São Francisco Craton.
This might indicate that smoothness regularization should not be applied
indiscriminately to the whole model, as suggested by the CRUST1.0 synthetic
data test.
Another reason for the observed misfit might be the presence of crustal or
mantle density anomalies whose gravitational effects were not removed during
the data corrections.
In the Guyana Basin on the coastal region of Venezuela, along the central
Amazonas and Solimões Basins, and in the Paraná Basin, our Moho depth model is
able to fit the gravity data but differs significantly from the seismic data.
These discrepancies in the Paraná and Amazonas Basins are interpreted in the
literature as high density rocks in the lower crust.
In general, differences between a gravity and a seismically derived Moho model
may indicate the presence of crustal or mantle density anomalies that were
unaccounted for in the data processing.
Such locations warrant further detailed investigation.

@@

We are indebted to the developers and maintainers of the open-source
software without which this work would not have been possible.
We thank Dr. Marcelo Assumpção for providing the seismological Moho depth
estimates,
Editor Dr. Gary Egbert and two anonymous reviewers for their thoughtful
comments that helped improve this work.
L. Uieda was supported by a scholarship from
Coordenação de Aperfeiçoamento de Pessoal de Nível Superior
(CAPES).
V.C.F. Barbosa was supported by a fellowship from
Conselho Nacional de Desenvolvimento Científico e Tecnológico (CNPq).
